Fuels, fire weather, and Rx fire behavior in North Dakota

### 2021-02-08 writeups/FuelsWeatherFirebehavior.Rmd
add an .md file?

---
title: Fuels, fire weather, and Rx fire behavior in North Dakota
subtitle: 
date: '`r Sys.Date()`'
author: DAM
output:
  html_document:
    toc: true
    toc_float: true
    theme: united
    highlight: tango
---

>>>>

---
title: Fuels, fire weather, and Rx fire behavior in North Dakota
subtitle: 
date: '`r Sys.Date()`'
author: DAM
output:
  html_document:
    keep_md: true
    toc: true
    toc_float: true
    theme: united
    highlight: tango
---
